Chum Populations

### 2015-11-28 paper/main.tex
roate PCA axes to match
update tables 1 and 2

\pagebreak
\section*{Figures}
\subsection*{Map of sampling locations including run timing}
\begin{figure}[H]
\includegraphics[scale=.6]{figures/collection_map.png}
\caption[Collection locations]{Collection locations and runtiming of chum salmon sampled near Puget Sound.}
\end{figure}

@@

\subsection*{Population structure}
\begin{figure}[H]
\includegraphics[scale=.35]{figures/poster_3a.png}
\includegraphics[scale=.35]{figures/poster_3b.png}
\includegraphics[scale=.35]{figures/poster_3c.png}
\caption[Individual-based PCAs showing population structure]{Population structure - Individual-based PCA from ten populations (colors) of chum salmon from Puget Sound.  Population structure obtained from paralogs (a) is similar to that obtained by non-paralogs (b), especially after down-sampling to match the number of loci (c).}
\end{figure}

@@

\subsection*{Sequencing and genotyping}

\begin{table}[H]
\caption{\label{tab:table-name}Sample sizes. usable sequences, and genotyping rates}

\begin{tabular}{lrrrrr}
\toprule
{} & {} & \multicolumn{2}{c}{Aligned sequences} & \multicolumn{2}{c}{Genotyping rate}\\
Collection &  n   &            mean &        std &              mean &       std \\
\midrule
Hamma Hamma            &  20 &         1,419,541 & 1,427,760 &            0.87 &       0.08 \\
Lilliwaup Creek        &  20 &         2,760,125 &   999,141 &            0.98 &       0.01 \\
Nisqually Kalama Creek &  17 &         2,270,022 & 1,432,866 &            0.96 &       0.03 \\
Sherwood River Fall    &  32 &         3,235,188 &   966,091 &            0.96 &       0.04 \\
Sherwood River Summer  &  31 &         2,504,974 & 1,183,089 &            0.91 &       0.07 \\
Skookum Creek          &  11 &         1,644,932 &   637,844 &            0.95 &       0.09 \\
Snohomish River        &  14 &         1,135,085 &   495,888 &            0.94 &       0.07 \\
Squakum Creek          &   8 &           999,084 &   650,927 &            0.86 &       0.08 \\
Stillaguamish River    &  13 &           710,538 &   269,873 &            0.91 &       0.06 \\
\midrule
Hoodsport Hatchery*    &   8 &           509,422 &   148,391 &            0.85 &       0.08 \\
\bottomrule
\multicolumn{6}{l}{*paired-end sequencing.}
5\end{tabular}

\end {table}

\subsection*{Genetic diversity}

\begin{table}[H]
%\caption{\label{tab:table-name}Genetic diversity}
\caption{Genetic diversity} 
\begin{tabular}{lrr}
\toprule
{} & Heterozygosity &     Ne \\
\midrule
Hamma Hamma            &           0.30 &    339 \\
Lilliwaup Creek        &           0.34 &  5,959 \\
Nisqually Kalama Creek &           0.32 &    161 \\
Sherwood River Fall    &           0.33 &    319 \\
Sherwood River Summer  &           0.31 &    145 \\
Skookum Creek          &           0.33 &  1,788 \\
Snohomish River        &           0.32 &  2,122 \\
Squakum Creek          &           0.31 & $\infty$* \\
Stillaguamish River    &           0.30 &  1,001 \\
\midrule
Hoodsport Hatchery     &           0.30 & $\infty$* \\
\bottomrule
\multicolumn{3}{l}{*small sample size (\textless10)}
\end{tabular}

\end {table}

>>>>

\pagebreak
\section*{Figures}
\subsection*{Map of sampling locations including run timing}
\begin{figure}[H]
\includegraphics[scale=.6]{figures/collection_map_colors.png}
\caption[Collection locations]{Collection locations and runtiming of chum salmon sampled near Puget Sound.}
\end{figure}

@@

\subsection*{Population structure}
\begin{figure}[H]
\includegraphics[scale=.35]{figures/PCA_a.png}
\includegraphics[scale=.35]{figures/PCA_b.png}
\includegraphics[scale=.35]{figures/PCA_c.png}
\includegraphics[scale=.45]{figures/PCA_legend.png}
\caption[Individual-based PCAs showing population structure]{Population structure - Individual-based PCA from ten populations (colors) of chum salmon from Puget Sound.  Population structure obtained from paralogs (a) is similar to that obtained by non-paralogs (b), especially after down-sampling to match the number of loci (c).}
\end{figure}

@@

% Table 1
\begin{table}[H]
\caption{\label{tab:table-name}Sample size. usable sequences, and genotyping rate for each collection}
\begin{tabular}{llrrrrrr}
\toprule
{} & {} & {} & {} & \multicolumn{2}{c}{Usabled sequences} & \multicolumn{2}{c}{Genotyping rate}\\
Collection &  Run Timing   &  Year &  n &          mean &        std &              mean &       std \\
\midrule
Hamma Hamma            &  Summer &  2010 &  20 &         1,419,541 & 1,427,760 &            0.87 &       0.08 \\
Lilliwaup Creek        &    Fall &  2011 &  20 &         2,760,125 &   999,141 &            0.98 &       0.01 \\
Nisqually Creek &  Winter &  2003 &  17 &         2,270,022 & 1,432,866 &            0.96 &       0.03 \\
Sherwood River     &    Fall &  1994 &  32 &         3,235,188 &   966,091 &            0.96 &       0.04 \\
Sherwood River   &  Summer &  1994 &  31 &         2,504,974 & 1,183,089 &            0.91 &       0.07 \\
Skookum Creek          &    Fall &  2010 &  11 &         1,644,932 &   637,844 &            0.95 &       0.09 \\
Snohomish River        &    Fall &  2010 &  14 &         1,135,085 &   495,888 &            0.94 &       0.07 \\
Squakum Creek          &     Fall &  2010 &   8 &           999,084 &   650,927 &            0.86 &       0.08 \\
Stillaguamish River    &    Fall &  2010 &  13 &           710,538 &   269,873 &            0.91 &       0.06 \\
\midrule
Hoodsport Hatchery     &    Fall &  2010 &   8 &           509,422 &   148,391 &            0.85 &       0.08 \\
\bottomrule
\multicolumn{6}{l}{*paired-end sequencing.}
\end{tabular}
\end {table}

% Table 2
\begin{table}[H]
\caption{Genetic diversity} 
\begin{tabular}{lrrll}
\toprule
Collection & Obs. Het. &  $\widehat{N_{e}}$ &   lower CI &    upper CI \\
\midrule
Hamma Hamma            &           0.30 &    339 &   316.5 &    365.8 \\
Lilliwaup Creek        &           0.34 &  5,959 &  3276.5 &  32651.6 \\
Nisqually Kalama Creek &           0.32 &    161 &   156.7 &    166.8 \\
Sherwood River (Fall)    &           0.33 &    319 &   310.8 &    329.5 \\
Sherwood River (Summer)  &           0.31 &    145 &   142.9 &    147.6 \\
Skookum Creek          &           0.33 &  1,788 &  1121.0 &   4402.6 \\
Snohomish River        &           0.32 &  2,122 &  1400.1 &   4379.3 \\
Squakum Creek          &           0.31 & $\infty$* &     NA &      NA \\
Stillaguamish River    &           0.30 &  1,001 &   766.0 &   1443.7 \\
\midrule
Hoodsport Hatchery     &           0.30 & $\infty$* &     NA &      NA \\
\bottomrule
\multicolumn{3}{l}{*small sample size (\textless10)}
\end{tabular}
\end {table}
